Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
tilde tests

\begin{figure}[t]
  \begin{align}
    v & ::= x \: | \: k \: | \: \textsf{fix} f . \lambda x . e \tag*{ } \\
    v' & ::= x \: | \: k \: | \: \textsf{fix} f . \lambda x . e' \: | \: <v | v> \tag{values}\\
    a & ::= v \tag*{ } \\
    a' & ::= a \: | \: <a | a> \tag{answers} \\
    e & ::= a \: | \: v v \: | \: \textsf{if } v \: e \: e \: | \: \textsf{let
    } x := v \textsf{ in } e \tag*{ } \\
    e' & ::= a' \: | \: v' v' \: | \: \textsf{if } v' \: e' \: e' \: | \:
    \textsf{let } x := v' \textsf{ in } e' \: | \: <e | e> \tag{expressions}
  \end{align}
  \caption{Syntax of \langName.  The prime variants are the full class of
  expressions, values, and answers.  This construction avoids allowing nested
  branching values.}
  \label{fig:syntax}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{align}
    v & ::= x \: | \: k \: | \: \textsf{fix} f . \lambda x . e \tag*{ } \\
    v' & ::= v \: | \: <v | v> \tag{values}\\
    a & ::= v \tag*{ } \\
    a' & ::= a \: | \: <a | a> \tag{answers} \\
    e & ::= a \: | \: v v \: | \: \textsf{if } v \: e \: e \: | \: \textsf{let
    } x := v \textsf{ in } e \tag*{ } \\
    e' & ::= e \: | \: <e | e> \tag{expressions}
  \end{align}
  \caption{Syntax of \langName.  The prime variants are the full class of
  expressions, values, and answers.  This construction avoids allowing nested
  branching values.}
  \label{fig:syntax}
\end{figure}
